---
title: "lab7"
author: "Bowen_Yao"
date: "2016/10/3"
output: html_document
---

#Single variable non-linear method
Linear model to predict wage using age
```{r}
library(ISLR)
attach(Wage)
fit=lm(wage~poly(age,degree=4,raw=T),data=Wage)
coef(summary(fit))
```

Predict and boundaries
```{r}
agelims=range(age)
age.grid=seq(from=agelims[1],to=agelims[2])
preds=predict(fit,newdata=list(age=age.grid),se=T)
se.bands=cbind(preds$fit+2*preds$se.fit,preds$fit-2*preds$se.fit)
```

Plot
```{r}
plot(age,wage,xlim=agelims,col="darkgrey")
title("Degree -4 Polynomial", out=T)
lines(age.grid,preds$fit,lwd=2,col="blue")
matlines(age.grid,se.bands,lwd=1,col="blue",lty=3)
```

Use ANOVA to determine the degree of the poly to use.
```{r}
fit.1=lm(wage~age,data=Wage)
fit.2=lm(wage~poly(age,2),data=Wage)
fit.3=lm(wage~poly(age,3),data=Wage)
fit.4=lm(wage~poly(age,4),data=Wage)
fit.5=lm(wage~poly(age,5),data=Wage)
anova(fit.1,fit.2,fit.3,fit.4,fit.5)
```

Logistic Regression to predict whether wage>250 using age
```{r}
fit=glm(I(wage>250)~poly(age,4),data=Wage,family=binomial)
preds=predict(fit,newdata=list(age=age.grid),se=T)
pfit=exp(preds$fit)/(1+exp(preds$fit))
se.bands.logit=cbind(preds$fit+2*preds$se.fit,preds$fit-2*preds$se.fit)
se.bands=exp(se.bands.logit)/(1+exp(se.bands.logit))
```

Plot
```{r}
plot(age,I(wage>250),xlim=agelims,type="n",tylim=c(0,.2))
points(jitter(age),I((wage>250)/5),cex=0.5,pch="|",col="darkgrey")
lines(age.grid,pfit,lwd=2,col="blue")
matlines(age.grid,se.bands,lwd=1,col="blue",lty=3)
```

Use step function to predict wage using age
```{r}
chunck=cut(age,4)
table(chunck)
fit=lm(wage~chunck,data=Wage)
newChuck=cut(age.grid,4)
preds=predict(fit,newdata = list(chunck=newChuck),se=T)
se.bounds=cbind(preds$fit+2*preds$se.fit,preds$fit-2*preds$se.fit)
```

Plot
```{r}
plot(age,wage,xlim=agelims,col="darkgrey")
lines(age.grid,preds$fit,lwd=2,col="blue")
matlines(age.grid,se.bounds,lwd=1,col="blue",lty=3)
```

Use splines to predict wage using age
```{r}
library(splines)
fit=lm(wage~bs(age,knots=c(25,40,60)),data=Wage)
preds=predict(fit,newdata=list(age=age.grid),se=T)
se.bounds=cbind(preds$fit+2*preds$se.fit,preds$fit-2*preds$se.fit)
```

Plot
```{r}
plot(age,wage,xlim=agelims,col="darkgrey")
lines(age.grid,preds$fit,lwd=2,col="blue")
matlines(age.grid,se.bounds,lwd=1,col="blue",lty=3)
```

Use nature splines to predict wage using age
```{r}
fit=lm(wage~ns(age,df=6),data=Wage)
preds=predict(fit,newdata=list(age=age.grid),se=T)
se.bounds=cbind(preds$fit+2*preds$se.fit,preds$fit-2*preds$se.fit)
```

Plot
```{r}
plot(age,wage,xlim=agelims,col="darkgrey")
lines(age.grid,preds$fit,lwd=2,col="blue")
matlines(age.grid,se.bounds,lwd=1,col="blue",lty=3)
```

Use smoothing splines to predict wage using age
```{r}
fit=smooth.spline(age,wage,df=16)
fit2=smooth.spline(age,wage,cv=T)
fit2$df
preds=predict(fit,newdata=list(age=age.grid),se=T)
```

Plot
```{r}
plot(age,wage,xlim=agelims,col="darkgrey")
#lines(age.grid[2:62],preds$y,col="red",lwd=2)
lines(fit,col="red",lwd=2)
lines(fit2,col="blue",lwd=2)
legend("topright",legend=c("DF 16","CV: DF 6.8"),col=c("red","blue"),lty=1,lwd=2,cex=0.8)
```

Use local regression to predict wage using age
```{r}
fit=loess(wage~age,span=0.2,data=Wage)
fit2=loess(wage~age,span=0.5,data=Wage)
preds=predict(fit,data.frame(age=age.grid))
preds2=predict(fit2,data.frame(age=age.grid))
```

Plot
```{r}
plot(age,wage,xlim=agelims,col="darkgrey")
lines(age.grid,preds,col="red",lwd=2)
lines(age.grid,preds2,col="blue",lwd=2)
legend("topright",legend=c("Span=0.2","Span=0.5"),col=c("red","blue"),lty=1,lwd=2,cex=0.8)
```

#Multivariate non-linear method--Generalized Additive Model

###If all of the single variable models can be expressed using a basis functions
```{r}
gam1=lm(wage~ns(year,df=4)+bs(age,df=5)+education,data=Wage)
```

###If not, such as smoothing splines, we need the gam library
```{r}
library(gam)
gam2=gam(wage~s(year,4)+s(age,5)+education,data=Wage)
gam3=gam(wage~s(year,4)+lo(age,span=0.7)+education,data=Wage)
gam4=gam(I(wage>250)~s(year,4)+lo(age,span=0.7)+education,family=binomial,data=Wage)
par(mfrow=c(1,3))
plot.gam(gam1,se=T,col="blue")
plot.gam(gam2,se=T,col="red")
plot.gam(gam3,se=T,col="green")
plot.gam(gam3,se=T,col="grey")
```

We can also include interaction using local weighted regression:
```{r}
gam.i=gam(wage~lo(year,age,span=0.5)+education,data=Wage)
library(akima)
plot(gam.i)
```

